Automated Design of Nanophotonic Waveguide Couplers

### 2011-10-07 presentations/ob1_wg_paper/paper.tex
Added a bunch of figures.

% Coupling efficiency
% Design time
% Size of the device
% Frequency
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{fig/fiber} 
    \caption{Waveguide coupler for a wide, low-index waveguide. 
        The dielectric structure of the coupler and surrounding input and
        output waveguides is shown on the left, while the simulation
        validating our results is shown on the right.
        The coupler converts $96.3\%$ of the input power to the
        designated output mode.
        The device is extremely compact, 
        convering only $36 \times 66$ grid points,
        where the vacuum wavelength is 42 grid points.
        Computation time was 20 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{fig/mode-conv} 
    \caption{Coupler that converts the fundamental waveguide mode to the
        second-order waveguide mode.
        This problem is quite difficult since the two modes are of 
        opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
        (which has the same dimensions and vacuum wavelength as Fig. 1) 
        which achieves a coupling efficiency of $95.5\%$. 
        Computation time was extended to 50 minutes to improve efficiency.
        }
    \label{fig:mode}
    \end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{fig/air-core}
    \caption{Coupler to an air-core mode.
        Here, not only are the modes of opposite symmetry,
        but the output waveguide operates on a fundamentally different
        principle (guided by Bragg reflection) than the input waveguide 
        (index guided).
        The device still achieves an efficiency of $83.3\%$, demonstrating the
        versatility of our method.
        The vacuum wavelength is 25 grid points, 
        while the device footprint is still $36 \times 66$ grid points.
        Computation time was 20 minutes.
        }
        \label{fig:aircore}
\end{figure}

>>>>

% For all designs mention
% fast - 20 minutes
All results were obtained in 20 minutes on a single-core personal computer
% subwavelength? all use only 1-4 square vacuum wavelengths
% high performance

% Special mention (arbitrariness)
% breaking symmetry for figs 2, and 3
% fig 3 is not even index guided

% Starting point given just by e = 9
% Mention thresholding efficiencies.

% Coupling efficiency
% Design time
% Size of the device
% Frequency
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{quickfig/fiber} 
    \caption{Waveguide coupler for a wide, low-index 
        ($\epsilon=2.25$) waveguide. 
        The dielectric structure of the coupler and surrounding input and
        output waveguides is shown on the left, while the simulation
        validating our results is shown on the right.
        The coupler converts $96.3\%$ of the input power to the
        designated output mode.
        The device is extremely compact, 
        convering only $36 \times 66$ grid points,
        where the vacuum wavelength is 42 grid points.
        Computation time was 20 minutes on a personal computer.}
    \label{fig:fiber}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{quickfig/mode-conv} 
    \caption{Coupler that converts the fundamental waveguide mode to the
        second-order waveguide mode.
        This problem is quite difficult since the two modes are of 
        opposite symmetry.
        For example, adiabatic approaches cannot be applied to this case.
        However, our method produces a device 
        (which has the same dimensions and vacuum wavelength as Fig. 1) 
        which achieves a coupling efficiency of $95.5\%$. 
        Computation time was 20 minutes on a personal computer. (movie?)
        }
    \label{fig:mode}
    \end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{quickfig/air-core}
    \caption{Coupler to an air-core mode.
        Here, not only are the modes of opposite symmetry,
        but the output waveguide operates on a fundamentally different
        principle (guided by Bragg reflection) than the input waveguide 
        (index guided).
        The device still achieves an efficiency of $83.3\%$, demonstrating the
        versatility of our method.
        The vacuum wavelength is 25 grid points, 
        while the device footprint is still $36 \times 66$ grid points.
        Computation time was 20 minutes on a personal computer.
        }
        \label{fig:aircore}
\end{figure}
